Tracing the Stellar Halo of Massive Galaxies to 100 kpc at $0.3<z<0.5$ using the Hyper Suprime-Cam

### 2017-05-31 draft/paper1_jenny.tex
Edit SMF

    In Section \ref{ssec:mtotal}, we demonstrate that different methods for estimating
    ``total'' \mstar{} can have a large impact at the high-mass end.

    Different methods for estimating the ``total'' \mstar{} can have a large impact on 
    the high mass end of the galaxy stellar mass function (e.g. \citealt{Bernardi2013, 
    DSouza2014, DSouza2015, Bernardi2016a}). 
    Fig~\ref{fig:mass_complete} shows the SMF computed using both \mtot{} and \mcmodel{}. 
    As can be seen from this figure, our careful 1-D approach recovers more flux 
    in massive galaxies than \texttt{cModel}. 
    More importantly, the average difference steadily increases with \mtot{}. 
    At \logms{} $>11.5$, the difference can be larger than 0.2 dex. 
    This difference relates to the intrinsic limitation of the \texttt{cModel} method 
    and also reflects the fact that more massive ETGs tend to have more extended 
    stellar mass distributions (e.g. \citealt{Graham2003}). 
    Generally speaking, the use of \mtot{} instead of the \mcmodel{} shifts the SMF 
    towards the higher-mass end and slightly modifies the high-mass slope. 
    %The impact of missing flux is most prominent for the \rbcg{} sample.
    For studies about the SMF or other aspects of galaxy evolution based on 
    \cmodel{}-like photometry or shallower images, these effects can not be neglected.

    How to define and measure the ``total'' mass of a galaxy becomes a critical 
    question when studying the high-mass end of the galaxy SMF. 
    The issues discussed above are currently one of the primary limitations in 
    determinations of the high-mass end of the SMF (\citealt{Bernardi2016}). 
    Fig~\ref{fig:mass_complete} illustrated how improved \mstar{} measurement can 
    significantly modifies the SMF. 
    On the right hand side of Fig~\ref{fig:smf}, we further highlight that 
    the shape of SMF at high-mass end is quite sensitive to even very small 
    change of \mstar{}. 
    We also compare the SMFs of our HSC samples with the following previous studies:

@@

%% ------------------------------------------------------------------------------------ %% 
    It is clear that different analyses lead to very different slopes at high-mass end. 
    Here, we do not try to evaluate whether the differences displayed in 
    Fig~\ref{fig:smf} are dominated by differences in photometry versus 
    assumptions about stellar population models (e.g. \citealt{Bernardi2016}). 
    However, given that the results that we are comparing assume the same IMF and adopt 
    similar assumptions about stellar population models, we hypothesize that the 
    differences in Fig~\ref{fig:smf} are dominated by differences in photometry. 
    The goal of our of present paper is not to present and discuss a careful evaluation
    of the high-mass end of the SMF -- this will be presented in a forthcoming paper 
    once the HSC survey has accumulated more data. 
    However, this is clearly a topic that warrants further investigation, and careful 
    photometry measurements from HSC data will shed further light on these questions.

@@

%% ------------------------------------------------------------------------------------ %% 
	In addition to the shape of the light profile, we can also 
    study the $k$-corrected color profiles and ellipticity profiles 
    (computed via \texttt{Ellipse}) of these galaxies, and how 
    they depend on mass and environment.
    These quantities contain interesting information about the physical processes that 
    shape galaxies. We also want to be sure that we do not introduce any systematic bias in 
    our mass determinations because of systematic changes in color profile with stellar or 
    halo mass.

@@

    How to define and measure the ``total'' mass of a galaxy becomes a critical 
    question when studying the high-mass end of the galaxy SMF. 
    The issues discussed above are currently one of the primary limitations in 
    determinations of the high-mass end of the SMF (\citealt{Bernardi2016}). 
    Fig~\ref{fig:mass_complete} illustrated how improved \mstar{} measurement can 
    significantly modifies the SMF. 
    On the right hand side of Fig~\ref{fig:smf}, we further highlight that 
    the shape of SMF at high-mass end is quite sensitive to even very small 
    change of \mstar{}. 
    We also compare the SMFs of our HSC samples with the following previous studies:

@@

%% ------------------------------------------------------------------------------------ %% 
    It is clear that different analyses lead to very different slopes at high-mass end. 
    Here, we do not try to evaluate whether the differences displayed in 
    Fig~\ref{fig:smf} are dominated by differences in photometry versus 
    assumptions about stellar population models (e.g. \citealt{Bernardi2016}). 
    However, given that the results that we are comparing assume the same IMF and adopt 
    similar assumptions about stellar population models, we hypothesize that the 
    differences in Fig~\ref{fig:smf} are dominated by differences in photometry. 
    The goal of our of present paper is not to present and discuss a careful evaluation
    of the high-mass end of the SMF -- this will be presented in a forthcoming paper 
    once the HSC survey has accumulated more data. 
    However, this is clearly a topic that warrants further investigation, and careful 
    photometry measurements from HSC data will shed further light on these questions.

>>>>

    As one of the most fundamental statistics of galaxy population, the Stellar 
    Mass Function (SMF) and its evolution are critical to our understanding of 
    galaxy evolution.  
    In Section \ref{ssec:mtotal}, we demonstrate that different methods for estimating
    ``total'' \mstar{} can lead to quite different results, hence have a large impact 
    on the high mass end of the galaxy stellar mass function (e.g. 
    \citealt{Bernardi2013, DSouza2014, DSouza2015, Bernardi2017}).
    On average, integration of our carefully derived non-parametric \mden{} profile 
    to 100 kpc (\mtot{}) recovers more light (hence mass) than the \texttt{cModel}
    method. 
    At \logmtot{} $>11.6$, the difference sometimes can be larger than 0.2 dex. 
    More importantly, the average difference steadily increases with \mtot{}. 
    These differences relates to the intrinsic limitation of the \texttt{cModel} 
    method and also reflects the fact that more massive ETGs tend to have more 
    extended stellar mass distributions (e.g. higher-\ser{} index, 
    \citealt{Graham2003}).

    Although we do not attempt to measure SMF, we use Fig \ref{fig:smf}
    to demonstrate the impacts from missing light and different definitions of 
    \mstar{}.
    The left panel of Fig \ref{fig:smf} shows the SMF\footnote{There are actually
    the volume density distributions, we refer to them as SMFs for convenience 
    although the incompleteness and other systematics have not been corrected}
    computed using \mcmodel{} and \mtot{} for both the \rbcg{} and \nbcg{} samples.

    Generally speaking, the use of \mtot{} instead of the \mcmodel{} shifts the SMF 
    towards the higher-mass end without significantly modifying the slope at 
    high-mass end.
    Interestingly, the impact of missing flux is more prominent for the \rbcg{} 
    galaxies whose contribution to the very high-mass end is substantial. 
    This difference between the \rbcg{} and \nbcg{} samples here may hint that 
    the \rbcg{} galaxies suffer more from missing light. 
    We will look into this in details in the following work (Huang\etal in prep.).

    As discussed in Section~\ref{ssec:mtotal}, even with much deeper images from HSC,
    it is non-trivial to clearly define and measure the ``total'' \mstar{} for 
    these massive systems, and the \mden{} profiles of these galaxies often extend 
    well beyond 100 kpc. 
    We measure \mmax{} by integrating the \mden{} profiles out to the detection 
    limit that is defined by the background noise.
    Although the \mden{} profile becomes more uncertain at $>100$ kpc, \mmax{} can
    provide us certain clue about how much extra mass is ``hidden'' there. 
    Although the average difference we find is small even at high-mass end 
    (${\sim}0.03$ dex), on the right panel of Fig \ref{fig:smf}, we can still its 
    influence on the SMF at high-mass end, where the slope becomes slightly 
    shallower.

    % TODO: Move this to Paper II
    %In this work, we have opted to in general use \mtot{} rather than \mmax{} as the 
    %uncertainty on \mmax{} is larger. 
    %However, we have checked that none of our results are changed by replacing \mtot{} 
    %via \mmax{}.

    How to define and measure the ``total'' mass of a galaxy becomes a critical 
    question when studying the high-mass end of the galaxy SMF. 
    The issues discussed above are currently one of the primary limitations in 
    determinations of the high-mass end of the SMF (\citealt{Bernardi2017}). 
    Fig~\ref{fig:mass_complete} illustrated how improved \mstar{} measurement can 
    significantly modifies the SMF. 
    On the right hand side of Fig~\ref{fig:smf}, we further highlight that 
    the shape of SMF at high-mass end is quite sensitive to even very small 
    change of \mstar{}. 
    We also compare the SMFs of our HSC samples with the following previous studies:

@@

    Overall, this illustrates again that our 1-D approach has certain advantages 
    over the 2-D modeling method and in principle, should capture the majority of 
    the total \mstar{}.

    For studies about the SMF or other aspects of galaxy evolution based on 
    \cmodel{}-like photometry or shallower images, these effects can not be neglected.
%% ------------------------------------------------------------------------------------ %% 
    It is clear that different analyses lead to very different slopes at high-mass end. 
    Here, we do not try to evaluate whether the differences displayed in 
    Fig~\ref{fig:smf} are dominated by differences in photometry versus 
    assumptions about stellar population models (e.g. \citealt{Bernardi2017}). 
    However, given that the results that we are comparing assume the same IMF and adopt 
    similar assumptions about stellar population models, we hypothesize that the 
    differences in Fig~\ref{fig:smf} are dominated by differences in photometry. 
    The goal of our of present paper is not to present and discuss a careful evaluation
    of the high-mass end of the SMF -- this will be presented in a forthcoming paper 
    once the HSC survey has accumulated more data. 
    However, this is clearly a topic that warrants further investigation, and careful 
    photometry measurements from HSC data will shed further light on these questions.

@@

%% ------------------------------------------------------------------------------------ %% 
	The 1-D \mden{} profiles are extracted using single band image and the flux-weighted 
	shape of the isophote.  
	From the HSC images of these massive

	In addition to the shape of the light profile, we can also 
    study the $k$-corrected color profiles and ellipticity profiles 
    (computed via \texttt{Ellipse}) of these galaxies, and how 
    they depend on mass and environment.
    These quantities contain interesting information about the physical processes that 
    shape galaxies. We also want to be sure that we do not introduce any systematic bias in 
    our mass determinations because of systematic changes in color profile with stellar or 
    halo mass.

@@

    How to define and measure the ``total'' mass of a galaxy becomes a critical 
    question when studying the high-mass end of the galaxy SMF. 
    The issues discussed above are currently one of the primary limitations in 
    determinations of the high-mass end of the SMF (\citealt{Bernardi2017}). 
    Fig~\ref{fig:mass_complete} illustrated how improved \mstar{} measurement can 
    significantly modifies the SMF. 
    On the right hand side of Fig~\ref{fig:smf}, we further highlight that 
    the shape of SMF at high-mass end is quite sensitive to even very small 
    change of \mstar{}. 
    We also compare the SMFs of our HSC samples with the following previous studies:

@@

%% ------------------------------------------------------------------------------------ %% 
    It is clear that different analyses lead to very different slopes at high-mass end. 
    Here, we do not try to evaluate whether the differences displayed in 
    Fig~\ref{fig:smf} are dominated by differences in photometry versus 
    assumptions about stellar population models (e.g. \citealt{Bernardi2017}). 
    However, given that the results that we are comparing assume the same IMF and adopt 
    similar assumptions about stellar population models, we hypothesize that the 
    differences in Fig~\ref{fig:smf} are dominated by differences in photometry. 
    The goal of our of present paper is not to present and discuss a careful evaluation
    of the high-mass end of the SMF -- this will be presented in a forthcoming paper 
    once the HSC survey has accumulated more data. 
    However, this is clearly a topic that warrants further investigation, and careful 
    photometry measurements from HSC data will shed further light on these questions.
